---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, fig.retina = 2, message = FALSE, warning = FALSE
)
options(width=120)
```

# tsuka

## Description

## What's Inside The Tin

You need to install <https://github.com/hackers-painters/katana-parser> as a system library that is reachable by the R compilation defaults.

In `src/` there are some header files copied from the `katana` src which enable use of the same utility functions they use.

The following functions are implemented:

- `parse_css`: parse a CSS file into a data frame

## Usage

```{r lib-ex}
library(tsuka)

# current version
packageVersion("tsuka")

```

```{r}
parse_css(system.file("extdat/sample.css", package = "tsuka"))
```

## tsuka Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
